Reproducibility and Open Science in Economics

### 2025-07-17 article.tex
Typos

As a first step, these downloads were mapped to countries, and then aggregated by regions (Table~\ref{tab:stata_downloads_regional_stats_2024} for Stata, Table~\ref{tab:r_downloads_regional_stats_2024} for R).
%
%
\input{outputs/stata_downloads_regional_stats_select}
\input{outputs/r_downloads_regional_stats_select}
%
Mapped onto a world map, this provides a pretty picture, though not very informative (Figure~\ref{fig:stata_r_world}).
\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{outputs/stata_downloads_world_map_2024_nochina.png}

    \includegraphics[width=0.8\textwidth]{outputs/r_downloads_world_map_2024_nochina.png}
    \caption{Downloads of Stata packages and R software, by region, without China. Source: published data by Kit Baum and Posit PBC, own calculations.}
    \label{fig:stata_r_world}
\end{figure}
The data suggest that downloads from China are not fully captured by the Posit-managed mirror, possibly because of peculiarities of the Chinese internet infrastructure. While this is possible for other countries as well, it is not fully detectable. I have excluded China from all calculations, but the remaining computations should be regarded as indicative as best.

I then aggregate countries and regions into "Global North" and "Global South" (Table~\ref{tab:stata_downloads_global_stats_2024_nochina} for Stata, Table~\ref{tab:r_downloads_global_stats_2024_nochina} for R). 
%
%
\input{outputs/stata_downloads_global_stats_select}
\input{outputs/r_downloads_global_stats_select}
%
%
Differencing the two tables  gives the relative importance of Stata versus R, namely that there are relatively more downloads of Stata packages in the Global North than there are of R binaries, suggesting (very tentatively) that Stata usage may be higher in the Global North (Table~\ref{tab:ns_compare})
Reverting back to smaller regions, however, paints the more nuanced picture referenced in the main text (Table~\ref{tab:region_compare}). Tables~\ref{tab:ns_compare} and~\ref{tab:region_compare} are summarized in Figure~\ref{fig:downloads} in the main text.

>>>>

As a first step, these downloads were mapped to countries, and then aggregated by regions (Table~\ref{tab:stata_downloads_regional_stats_select} for Stata, Table~\ref{tab:r_downloads_regional_stats_select} for R).
%
%
\input{outputs/stata_downloads_regional_stats_select}
\input{outputs/r_downloads_regional_stats_select}
%
Mapped onto a world map, this provides a pretty picture, though not very informative (Figure~\ref{fig:stata_r_world}).
\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{outputs/stata_downloads_world_map_select_nochina.png}

    \includegraphics[width=0.8\textwidth]{outputs/r_downloads_world_map_select_nochina.png}
    \caption{Downloads of Stata packages and R software, by region, without China. Source: published data by Kit Baum and Posit PBC, own calculations.}
    \label{fig:stata_r_world}
\end{figure}
The data suggest that downloads from China are not fully captured by the Posit-managed mirror, possibly because of peculiarities of the Chinese internet infrastructure. While this is possible for other countries as well, it is not fully detectable. I have excluded China from all calculations, but the remaining computations should be regarded as indicative as best.

I then aggregate countries and regions into "Global North" and "Global South" (Table~\ref{tab:stata_downloads_global_stats_select_nochina} for Stata, Table~\ref{tab:r_downloads_global_stats_select_nochina} for R). 
%
%
\input{outputs/stata_downloads_global_stats_select_nochina}
\input{outputs/r_downloads_global_stats_select_nochina}
%
%
Differencing the two tables  gives the relative importance of Stata versus R, namely that there are relatively more downloads of Stata packages in the Global North than there are of R binaries, suggesting (very tentatively) that Stata usage may be higher in the Global North (Table~\ref{tab:ns_compare})
Reverting back to smaller regions, however, paints the more nuanced picture referenced in the main text (Table~\ref{tab:region_compare}). Tables~\ref{tab:ns_compare} and~\ref{tab:region_compare} are summarized in Figure~\ref{fig:downloads} in the main text.
